---
title: "Overview of `pwtest()`"
author: "Clara Bicalho"
date: "2025-06-27"
output: 
  html_document:
    number_sections: false
---

Major changes to `pwtest()`

- Fully integrated with tidymodels and parsnip packages, so should be compatible with  all models and engines listed [here](https://www.tidymodels.org/find/parsnip/#models)
- Requires `model_spec` argument/object from parsnip package, where users specify models used to fit $Y^C(0)$. See `??parsnip::model_spec` for more details. This object should reflect a model chosen _after_ cross-validation, and allows for specification of tuning parameters.
- The engine (package) used to fit the model can be specified (e.g., "ranger", "randomForest", "glm"). Otherwise takes default engine for each `model_spec`.
- Formula can also be optionally specified. Defaults to `Y~.`.
- Exports: `pwdelta`, (defined by the observed $\widehat\overline{Y^T(0)} - \widehat{Y^C(0)}$), `pwdelta_se` and `pwdelta_p` (defined by bootstrap distribution), `fit_obj` the model fit object and `fit_metrics` containing standard metric statistics for the fit: mse, rsq, and mae

`pwtest()` no longer:

- Exports UW statistics (to be done by future `uwtest()` function)
- Exports stats like covariate weights, weights*dim for each covariate, etc. These were not being using anywhere in our analysis and won't be useful in practice.
- Performs tests of continuity (RD designs)/ These will be done  will be done by `pwtest_rdd()` since the anatomy of the function is entirely different.


```{r setup, message=FALSE, warning=FALSE}
library(pwtest)
library(tidymodels)
```

```{r, message=FALSE, warning=FALSE}
# Simulate polynomial structure DGP
source("~/Library/CloudStorage/Dropbox/Github-Cloud/prognostic_balance/code/simulations/R/simulate_experiment_poly_4.R")
data <- simulate_experiment(N = 1000, imbalance = rep(.2, 3), prognosis = c(.3, .2, .1), poly = c(2, 1))
```

## Method 1: lm

This is equivalent to our original PW (linear regression) specification

```{r}
pwtest(data, covariates = c("X1", "X2", "X1_2"), n_bootstraps = 200,
       model_spec = linear_reg()) # default engine of parsnip::linear_reg() is lm
```

## Method 2: random forest using package `ranger` (default of parsnip::rand_forest())

```{r}
pwtest(data, covariates = c("X1", "X2", "X1_2"), n_bootstraps = 200,
       model_spec = rand_forest(mode = "regression"))
```

## Method 3: random forest using package `randomForest`

```{r}
pwtest(data, covariates = c("X1", "X2", "X1_2"), n_bootstraps = 200,
       model_spec = rand_forest(mode = "regression"), engine = "randomForest")
```

# Method 4: glm using glmnet package

```{r}
pwtest(data, covariates = c("X1", "X2", "X1_2"),
                  model_spec = linear_reg(mode = "regression", penalty = .5), #requires penalty parameter
                  engine = "glmnet", n_bootstraps = 200, recipe = parsnip::recipe(data = data))
```



